Constraint Programming - Inside Gecode

### 2014-05-04 paper.tex
abstract

	\begin{abstract}	
		\textit{last thing to write}	
	\end{abstract}

>>>>

	\begin{abstract}	
		Gecode is one of the various tools for constraint programming, a well-studied area which aims to solve arbitrary combinatorial and optimzation problems. The basement for Gecode are variables, their domains, constraints on these variables and strategies to search for a solution space or only single solutions.
	\end{abstract}
